Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-18 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:18	14:28:11	(Tue18.Aug)

Assume that the wavefield has been sampled by an $M$ element uniform linear array, and that the signal signature has been removed by a matched filter. The data from the $m$th channel $x_m[\theta,n]$, where the azimuth angle $\theta$ and range sample $n$ is the focus point. To simplify notation, we make the dependence on $\theta$ implicit from now on. By definition, the beamformer output $z[n]$ can be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$.

@@

Note how subarray averaging led to a size reduction of $\eR$ from $\mathbb{C}^{M,M}$ to $\mathbb{C}^{L,L}$, and hence will produce an $L$-element weight set when substituted into (\ref{z}). This weight set is applied to all the subarrays, before computing the beamformer output as in (\ref{z}). Or, equivalently, we may apply the weight set to the sum of all the subarrays by
\begin{align}
z[n] = \w\H[n] \sumb{l=0}{M-L} \x_l[n].\label{finalZ}
\end{align}
% \ifPeerReview
% \begin{figure}[!t]\centering
% \includegraphics[width=.8\linewidth]{gfx/buske2\figPostfix.eps}
% \else
% \begin{figure}[!t]\centering
% \includegraphics[width=\linewidth]{gfx/implementation.eps}
% \fi%
% \caption{MVDR beamforming. For each pixel in range and azimuth:\newline
% 1. an $L\times{}L$ sample covariance matrix $\eR$ is computed; \newline
% 2. the term $\eR^{-1}\1$ is found using a linear equation solver;\newline
% 3. and the beamformer output $z$ is computed from (\ref{finalZ}), where $\w$ is found by substituting $\eR^{-1}\1$ into (\ref{weights}). } \label{mvdr_beamforming}
% \end{figure}
As summarized in Fig. \ref{mvdr_beamforming}, the MVDR method is applied to each pixel independently, by:
\begin{enumerate}
\item computing the sample covariance matrix $\eR$ in (\ref{finalR});
\item computing $\eRi\1$ in (\ref{weights});
\item computing the beamformer output $z$ in (\ref{finalZ}).
\end{enumerate}
Next we will evaluate these steps in terms of arithmetic complexity, and then discuss their mappability to parallel hardware.

@@

\section{Kaiser windows}

>>>>

Assume that the wavefield has been sampled by an $M$ element uniform linear array, and that the signal signature has been removed by a matched filter. Let $x_m[\theta,n]$ be the delayed data from the $m$th channel, where the $\theta$ and $n$ is the azimuth angle and range sample of the focus point, respectively. Each angle $\theta$ can be processed independently, so to simplify notation we will assume the dependence on $\theta$ to be implicit from now on.

The beamformer output $z[n]$ can now be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$. We will refer to a set of weights as a window, but it is also commonly called a taper function. Conventional beamformers all have static weights, and by far the most common of these is the delay-and-sum (DAS) beamformer, which does exactly what the name implies.

 See section \ref{kaiser_windows}.

@@

Note how subarray averaging led to a size reduction of $\eR$ from $\mathbb{C}^{M,M}$ to $\mathbb{C}^{L,L}$, and hence will produce an $L$-element weight set when substituted into (\ref{z}). This weight set is applied to all the subarrays, before computing the beamformer output as in (\ref{z}). Or, equivalently, we may apply the weight set to the sum of all the subarrays by
\begin{align}
z[n] = \w\H[n] \sumb{l=0}{M-L} \x_l[n].\label{finalZ}
\end{align}

Next we will evaluate these steps in terms of arithmetic complexity, and then discuss their mappability to parallel hardware.

@@

\section{Kaiser windows}\label{kaiser_windows}
